---
title: "Identify characters in transcripts"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

# Prepare session

```{r eval=TRUE, warning=FALSE, message=FALSE}

rm(list = ls())

library(stringr)
library(rebus)
library(magrittr)
library(tidyverse)

```

# Import data from previous scripts 

```{r eval=TRUE, warning=FALSE, message=FALSE}

episode.list.df <- read_rds("interim_output/episode_list_transcripts.RDS")

```


#Spot character names in transcripts
Transcriptions use names both in upper and lower case! 
e.g. 
* https://genius.com/Game-of-thrones-winter-is-coming-annotated
* https://genius.com/Game-of-thrones-the-kingsroad-annotated

Ideally, the pattern used should also be able to capture all names in characters scraped from wikipedia (i.e. object: characters.all).

There are some transcripts that use \ n pattern, others that don't

There are patterns of 'NAME (in valerian)' e.g:
'CERSEI (sighs): Thank you so much for your kind words'.

Names can have one or multiple words.

**TO DO: names can be preceeded by an interrogation mark in previous line. **
TO DO: this has to be changed to any character, including "-"

## Pattern to detect and extract character names 
```{r eval=TRUE, warning=FALSE, message=FALSE}

pattern.character.names <- rebus::or("\\.[[:alpha:]]+" %R% rebus::one_or_more(" [[:alpha:]]+") %R% ":",
"\n[[:alpha:]]+" %R% rebus::one_or_more(" [[:alpha:]]+") %R% ":",
"\n[[:alpha:]]+" %R% rebus::zero_or_more(" [[:alpha:]]+") %R% " \\(" %R% rebus::one_or_more(rebus::or("[[:alpha:]]","\\s")) %R% "\\):",
"\\.[[:alpha:]]+" %R% rebus::zero_or_more(" [[:alpha:]]+") %R% " \\(" %R% rebus::one_or_more(rebus::or("[[:alpha:]]","\\s")) %R% "\\):")

```

**Export pattern to next script**
```{r eval=TRUE, warning=FALSE, message=FALSE}

pattern.character.names %>% 
  write_rds("interim_output/regex_pattern_identify_characters_transcripts.RDS")

```


## Alternative pattern (space to check alternative patterns)
TO DO: this has to be changed to any character, including "-"

```{r eval=TRUE, warning=FALSE, message=FALSE}

alternative.pattern <- rebus::or( rebus::or("[[:punct:]]","\\s","\n") %R% "[[:alpha:]]+" %R% rebus::one_or_more(" [[:alpha:]]+") %R% ":",
           rebus::or("[[:punct:]]","\\s","\n") %R% "[[:alpha:]]+" %R% rebus::zero_or_more(" [[:alpha:]]+") %R% " \\(" %R% rebus::one_or_more(rebus::or("[[:alpha:]]","\\s")) %R% "\\):")

```



**Export alternative pattern to next script**
```{r eval=TRUE, warning=FALSE, message=FALSE}

alternative.pattern %>% 
  write_rds("interim_output/regex_alternative_pattern_identify_characters_transcripts.RDS")

```


## Apply pattern to obtain characters

** Main pattern**
```{r eval=TRUE, warning=FALSE, message=FALSE}

characters.transcripts <- episode.list.df$transcript %>%
str_extract_all(pattern = pattern.character.names) %>%
unlist %>% str_replace_all(pattern = rebus::or(":", "\n", "\\.", 
"\\(" %R% rebus::one_or_more("[[:print:]]") %R% "\\)"), replacement = "") %>% 
unique %>% 
sort

rm(pattern.character.names)

```

**Alternative pattern**
```{r eval=TRUE, warning=FALSE, message=FALSE}

characters.transcripts.alternative <- episode.list.df$transcript %>%
str_extract_all(pattern = alternative.pattern) %>%
unlist %>% str_replace_all(pattern = rebus::or(":", "\n", "\\.", "\\?", 
"\\(" %R% rebus::one_or_more("[[:print:]]") %R% "\\)"), replacement = "") %>% 
unique %>% 
sort

rm(alternative.pattern)

```

## Characters to upper
This is not the final list. Characters have to be cleaned in further scripts.
```{r eval=TRUE, warning=FALSE, message=FALSE}

characters.transcripts %<>%
toupper() %>% 
str_trim(side = "right") %>%
unique

characters.transcripts

```

## Export matched characters

```{r eval=TRUE, warning=FALSE, message=FALSE}

characters.transcripts %>%
  write_rds("interim_output/characters_matched_transcripts.RDS")

```


